\documentclass{article}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{longtable}
\usepackage[margin=0.75in]{geometry}

\begin{document}

\section*{Ontological Field Table: Equation of State Mapping}

\small
\rowcolors{2}{gray!10}{white}

\begin{longtable}{|>{\raggedright\arraybackslash}p{5cm}|>{\raggedright\arraybackslash}p{10cm}|}
\hline
\rowcolor{black!20}
\textbf{EoS Name} & \textbf{Definition} \\
\hline
Ideal Gas Law & Classical law for non-interacting gases; linear relation between pressure, volume, and temperature. \\
Van der Waals EoS & Corrected gas law including attractive forces and excluded volume. \\
Murnaghan EoS & Isothermal EoS for solids with pressure-dependent bulk modulus. \\
Birch-Murnaghan EoS & Finite-strain expansion used in high-pressure solid-state physics. \\
Vinet EoS & Empirical EoS accurate for extreme compressions. \\
Natural Strain EoS & Based on logarithmic (Hencky) strain; geometrically derived. \\
Polytropic EoS & Power-law relation between pressure and density, often in stellar systems. \\
Tait EoS & Empirical law for slightly compressible liquids. \\
Stiffened Gas EoS & Used for high-pressure multiphase simulations; includes reference pressure. \\
Mie-Grüneisen EoS & Internal energy-based EoS for dense matter under shock. \\
Chaplygin Gas & Negative-pressure fluid used in cosmology; DE/DM unification. \\
Barotropic Fluid & Pressure as a function of density only; no explicit temperature. \\
Quark-Gluon Plasma EoS & Derived from lattice QCD for high-energy phase transitions. \\
Hagedorn EoS & Postulated thermodynamic limit at high energy densities. \\
Relativistic EoS (TOV) & Coupled mass-density-pressure relation in curved spacetime. \\
DESI Parametric EoS & Observational, data-fitted $w(a)$ behavior of dark energy. \\
Geometric EoS (Jing-Chi-Shen) & Mass-volume-density as non-thermal state relation. \\
Shentegrity EoS & Recursive, topological, tensegrity-based relational model. \\
\hline
\end{longtable}

\end{document}
